\textbf{ Interpretable Gaussian Processes for Stellar Light Curves }

### 2020-08-04 tex/ms.tex
better english

%
\section{The Spot Expansion}
\label{sec:spot}
%
\subsection{Functional form}
%
We adopt the following expression for the spherical harmonic coefficient
of degree $l$ and order $m$ in the expansion of a spot at
$\theta = \varphi = 0$:
%
\begin{align}
    \label{eq:ylm0}
    y_{lm}(r, \delta) =
    \begin{cases}
        1 - \dfrac{\delta r'}{2 (1 + r')}
         & l = m = 0    \\[2em]
        -\dfrac{\delta r' \left( 2 + r' \right)}
        {2 \sqrt{2l + 1} (1 + r')^{l + 1}}
         & l > 0, m = 0 \\[2em]
        0
         & m \ne 0
    \end{cases}
\end{align}
%
where
%
\begin{align}
    \label{eq:rprime}
    r' \equiv c_0 + c_1 r
\end{align}
%
and $c_0, c_1 > 0$ are scaling constants (defined in more detail below).
In the expressions above,
$\delta \in (-\infty, 1]$ is the spot contrast (the fractional
decrease in the brightness
at the center of the spot) and $r \in [0, 1]$ is the normalized spot radius.
The expression in Equation~(\ref{eq:ylm0}) is convenient because it satisfies
five important properties:
%
\begin{enumerate}[itemsep=2pt,parsep=1pt,label=\textbf{\arabic*}]
    \item The surface intensity is azimuthally symmetric about the spot center
    \item The surface intensity monotonically increases away from the spot center
    \item The surface intensity at the spot center is $1 - \delta$
    \item The surface intensity at the antipode of the spot center is unity
    \item The size of the spot increases monotonically with $r$
\end{enumerate}
%
These properties may be demonstrated by considering the expression for the
surface intensity at a given point $(\theta, \varphi)$:
%
\begin{align}
    \begin{split}
        I(\theta, \varphi)
        & =
        \sum\limits_{l=0}^\infty \sum\limits_{m=-l}^l
        y_{lm} Y_{lm}(\theta, \varphi) \\
        & = \sum\limits_{l=0}^\infty
        y_{l0} \sqrt{2l + 1} P_l(\cos\theta)
    \end{split}
\end{align}
%
where $P_l$ is the Legendre polynomial of degree $l$ and we have implicitly
assumed a normalization such that the integral of our expansion over
the unit sphere is $4\pi$.
Note that the expression above is independent of the azimuth $\varphi$,
a consequence of the fact that all harmonics with $m \ne 0$ are zero; this
expansion is therefore azimuthally symmetric about the spot center, as
stated in \textbf{1}.
%
Combining the above expression with Equation~(\ref{eq:ylm0}) and
rearranging, we may write
%
\begin{align}
    \label{eq:Igen}
    I(\theta, \varphi) =
    I(\theta) =
    1 + \dfrac{\delta r'}{2}
    -
    \dfrac{\delta r' \left( 2 + r' \right)}{2 (1 + r')}
    \sum\limits_{l=0}^\infty \left(\dfrac{1}{1 + r'}\right)^l P_l(\cos\theta)
    \quad.
\end{align}
%
The summation in Equation~(\ref{eq:Igen}) has a closed-form expression in
terms of the generating function of the Legendre polynomials:
%
\begin{align}
    \label{eq:gen}
    \sum\limits_{l=0}^\infty t^l P_l(\cos\theta) = \frac{1}{\sqrt{1 + t^2 - 2 t \cos\theta}}
    \quad,
\end{align}
%
so we may express the intensity in the fairly simple form
%
\begin{align}
    \label{eq:Ifinal}
    I(\theta) & = A - \frac{B}{\sqrt{C - \cos\theta}}
    \quad,
    %
    \\
    \intertext{where}
    %
    \begin{split}
        A & = 1 + \dfrac{\delta r'}{2}                      \\
        B & = \delta r' (2 + r') \sqrt{\dfrac{1}{8 + 8 r'}} \\
        C & = \dfrac{1 + (1 + r')^2}{2 + 2 r'}
    \end{split}
\end{align}
%
are positive constants.

@@

\subsection{Behavior at finite degree}
%
The properties of the spot expansion described in the previous section
(in particular its monotonicity and values at the spot center and antipode)
are inherited from the generating function of the Legendre polynomials
(Equation~\ref{eq:gen}). These properties are therefore only rigorously
true when the expansion is taken to spherical
harmonic degree $l_{\mathrm{max}} = \infty$. For truncated expansions,
a value of $r'$ in Equation~(\ref{eq:ylm0}) that is too small will lead
to both ringing and a value at the spot center that is in general larger
than $1 - \delta$.

@@

\subsection{Distributions over $r$ and $\delta$}
%
We model the normalized spot radius $r$ as a random variable drawn from
a Beta distribution, whose PDF is given by
%
\begin{align}
    p \big(r \, \big| \, \alpha, \beta \big)
     & =
    \dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
    r^{\alpha - 1}
    (1 - r)^{\beta - 1}
    \quad,
\end{align}
%
where $\Gamma$ is the Gamma function and $\alpha$ and $\beta$ are
hyperparameters characterizing the shape of the distribution.
%
Since we require the brightness
%
\begin{align}
    b \equiv 1 - \delta
\end{align}
%
at the center of the spot to
be non-negative, it is convenient to treat $b \in [0, \infty)$ as our
random variable instead of $\delta$. We model $b$ as a random variable
drawn from a log-normal
distribution:
%
\begin{align}
    \label{eq:lognormal}
    p \big(b \, \big| \, \mu, \nu \big)
     & =
    \frac{1}{b\sqrt{2\pi\nu}}
    \exp\left[
        -\dfrac{\left(\ln b - \mu\right)^2}{2\nu}
        \right]
    \quad,
\end{align}
%
where $\mu$ and $\nu$ are the mean and variance of the log-normal, respectively.
The joint distribution over $r$ and $b$ is therefore separable,
by construction:
%
\begin{align}
    p \big( r, b \, \big| \, \alpha, \beta, \mu, \nu \big)
     & =
    p \big(r \, \big| \, \alpha, \beta \big)
    \,
    p \big(b \, \big| \, \mu, \nu \big)
    \quad.
\end{align}
%

\subsection{First moment}

@@

\subsection{Second moment}

>>>>

%
\section{The Spot Expansion}
\label{sec:spot}
%
\subsection{Preliminaries}
%
\subsubsection{Functional form}
\label{sec:spot-function}
%
We adopt the following expression for the spherical harmonic coefficient
of degree $l$ and order $m$ in the expansion of a spot at
$\theta = \varphi = 0$:
%
\begin{align}
    \label{eq:ylm0}
    y_{lm}(r, \delta) =
    \begin{cases}
        1 - \dfrac{\delta r'}{2 (1 + r')}
         & l = m = 0    \\[2em]
        -\dfrac{\delta r' \left( 2 + r' \right)}
        {2 \sqrt{2l + 1} (1 + r')^{l + 1}}
         & l > 0, m = 0 \\[2em]
        0
         & m \ne 0
    \end{cases}
\end{align}
%
where
%
\begin{align}
    \label{eq:rprime}
    r' \equiv c_0 + c_1 r
\end{align}
%
and $c_0, c_1 > 0$ are scaling constants (defined in more detail below).
In the expressions above,
$\delta \in (-\infty, 1]$ is the spot contrast (the fractional
decrease in the brightness
at the center of the spot) and $r \in [0, 1]$ is the normalized spot radius.
The expression in Equation~(\ref{eq:ylm0}) is convenient because it satisfies
six important properties:
%
\begin{enumerate}[itemsep=2pt,parsep=1pt,label=\textbf{\arabic*}]
    \item The surface intensity is azimuthally symmetric about the spot center
    \item The surface intensity monotonically increases away from the spot center
    \item The surface intensity at the spot center is $1 - \delta$
    \item The surface intensity at the antipode of the spot center is unity
    \item The size of the spot increases monotonically with $r$
\end{enumerate}
%
These properties may be demonstrated by considering the
expression for the surface intensity at a given point $(\theta, \varphi)$:
%
\begin{align}
    \begin{split}
        I(\theta, \varphi)
        & =
        \sum\limits_{l=0}^\infty \sum\limits_{m=-l}^l
        y_{lm} Y_{lm}(\theta, \varphi) \\
        & = \sum\limits_{l=0}^\infty
        y_{l0} \sqrt{2l + 1} P_l(\cos\theta)
    \end{split}
\end{align}
%
where $P_l$ is the Legendre polynomial of degree $l$ and we have implicitly
assumed a normalization such that the integral of our expansion over
the unit sphere is $4\pi$.
Note that the expression above is independent of the azimuth $\varphi$,
a consequence of the fact that all harmonics with $m \ne 0$ are zero; this
expansion is therefore azimuthally symmetric about the spot center, as
stated in \textbf{1}.
%
Combining the above expression with Equation~(\ref{eq:ylm0}) and
rearranging, we may write
%
\begin{align}
    \label{eq:Igen}
    I(\theta, \varphi) =
    I(\theta) =
    1 + \dfrac{\delta r'}{2}
    -
    \dfrac{\delta r' \left( 2 + r' \right)}{2 (1 + r')}
    \sum\limits_{l=0}^\infty \left(\dfrac{1}{1 + r'}\right)^l P_l(\cos\theta)
    \quad.
\end{align}
%
The summation in Equation~(\ref{eq:Igen}) has a closed-form expression in
terms of the generating function of the Legendre polynomials:
%
\begin{align}
    \label{eq:gen}
    \sum\limits_{l=0}^\infty t^l P_l(\cos\theta) = \frac{1}{\sqrt{1 + t^2 - 2 t \cos\theta}}
    \quad,
\end{align}
%
so we may express the intensity in the fairly simple form
%
\begin{align}
    \label{eq:Ifinal}
    I(\theta) & = A - \frac{B}{\sqrt{C - \cos\theta}}
    \quad,
    %
    \\
    \intertext{where}
    %
    \begin{split}
        A & = 1 + \dfrac{\delta r'}{2}                      \\
        B & = \delta r' (2 + r') \sqrt{\dfrac{1}{8 + 8 r'}} \\
        C & = \dfrac{1 + (1 + r')^2}{2 + 2 r'}
    \end{split}
\end{align}
%
are positive constants.

@@

\subsubsection{Behavior at finite degree}
%
The properties of the spot expansion described in the previous section
(in particular its monotonicity and values at the spot center and antipode)
are inherited from the generating function of the Legendre polynomials
(Equation~\ref{eq:gen}). These properties are therefore only rigorously
true when the expansion is taken to spherical
harmonic degree $l_{\mathrm{max}} = \infty$. For truncated expansions,
a value of $r'$ in Equation~(\ref{eq:ylm0}) that is too small will lead
to both ringing and a value at the spot center that is in general larger
than $1 - \delta$.

@@

\subsection{Probability distribution}
%
Our goal now is to characterize the distribution of $y_{lm}$ values as a
function of certain statistics of the spots: specifically, the distribution of
spot radii and intensities. As we will see, if we model these with a Beta and
a log-normal distribution, respectively, we may analytically compute the
first two moments of the distribution of $y_{lm}$ conditioned on the parameters
of these two prior distributions.

\subsubsection{Distributions over $r$ and $\delta$}
%
Since we require the normalized spot radius $r$ to be bounded
on the interval $[0, 1]$, we place a Beta prior on this quantity, whose
probability density function (PDF) is
%
\begin{align}
    p \big(r \, \big| \, \alpha, \beta \big)
     & =
    \dfrac{\Gamma(\alpha + \beta)}{\Gamma(\alpha)\Gamma(\beta)}
    r^{\alpha - 1}
    (1 - r)^{\beta - 1}
    \quad,
\end{align}
%
where $\Gamma$ is the Gamma function and $\alpha$ and $\beta$ are
hyperparameters characterizing the shape of the distribution.
%
And since we require the brightness
%
\begin{align}
    b \equiv 1 - \delta
\end{align}
%
at the center of the spot to
be non-negative, it is convenient to treat $b \in [0, \infty)$ as our
random variable instead of $\delta$. We therefore place a log-normal
prior on $b$, whose PDF is
%
\begin{align}
    \label{eq:lognormal}
    p \big(b \, \big| \, \mu, \nu \big)
     & =
    \frac{1}{b\sqrt{2\pi\nu}}
    \exp\left[
        -\dfrac{\left(\ln b - \mu\right)^2}{2\nu}
        \right]
    \quad,
\end{align}
%
where $\mu$ and $\nu$ are the mean and variance of the log-normal, respectively.
The joint distribution over $r$ and $b$ is therefore separable,
by construction:
%
\begin{align}
    p \big( r, b \, \big| \, \alpha, \beta, \mu, \nu \big)
     & =
    p \big(r \, \big| \, \alpha, \beta \big)
    \,
    p \big(b \, \big| \, \mu, \nu \big)
    \quad.
\end{align}
%
In the next two sections, we derive closed form expressions for the first
and second moments of the distribution
%
$p \big( y_{lm} \, \big| \, \alpha, \beta, \mu, \nu \big)$.

\subsubsection{First moment}

@@

\subsubsection{Second moment}
